The effect of genetic linkage on island endemics richness

### 2018-08-23 paper/draft.tex
discuss plant polyploidisation

[SPECULATION:] In mixed community scenarios this effect becomes less clear as inter-lineage competition and red-queen-dynamics
present complex challenges.

>>>>

In plants polyloidisation leads to increased speciation or adaptive radiation potential \cite{baduelPolyploidHopShifting2018}.
Although our model considers linkage and thus ploidy level as static, we still can draw some conclusions relevant to the issue
of why autopolyploids much rarer than paleopolyploids.
[in the beginning great variation, but as specialisation increases, mutations outcompeted]
[with high specialisation no evolutionary rescue in case of disturbance]
[SPECULATION:] In mixed community scenarios this effect becomes less clear as inter-lineage competition and red-queen-dynamics
present complex challenges.
